### 2021-04-23 input/conclusion.tex
reworkd conclusion

With the advent of the edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible trafic between \processes.  In this paper, we tackled
the problem of content indexing, a key service for storage systems.
%
More precisely, we proposed to address it as a dynamic logical partitioning of the infrastructure
that should be maintained according to replicas creations/removals and
infrastructure changes. Through an efficient scoped broadcast, each
\process composing the infrastructure knows eventually where the best
replica for a particular content is. The major difficulty is to handle
concurrent operations, each having a different scope, and ensure the
correct convergence of the system.
We defined, in particular,  multiple properties that highlight this complexity.
%
We proposed an implementation of this protocol called \NAME and
evaluated through simulations. Observations confirmed the
correctness of our protocol as well as the confinement of the traffic
only where it is needed.

As ongoing and future work, we are currently studying how it might be
possible to limit the scope of a partition to one autonomous system at
most. Indeed, the gain of propagating changes to \processes belonging to
another autonomous system might be negligible as the latency penalty
is mainly due to inter autonomous systems' links (\eg trans-continental
links).  Excatly, we are investigating how such a change can be
formalized and its impact on the current protocol.
%
%autonomous systems. Indeed, \processes could leverage the hierarchical
%properties of the Internet topology~\cite{nur2018geography} to avoid
%flooding the whole systems with control information about all
%partitions.
%\TODO{should we highlight this at the end of the experiment}
%
In addition to this action, it would make sense to evaluate the use of \NAME
within a concrete storage systems, such as
\underline{I}nter\underline{P}lanetary \underline{F}ile
\underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
integration would enabe us to to perform additional experiments and
observe the gain with respect to the DHT-based approach that is
currently used.

>>>>

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible traffic between \processes.  In this paper, we
tackled the problem of content indexing, a key service for storage
systems.
%
We proposed to address this problem as a dynamic logical partitioning
in dynamic networks where partitions grow and shrink to reflect
content and replicas locations, as well as infrastructure
changes. Using an efficient communication primitive called scoped
broadcast, each \process composing the infrastructure eventually knows
the \process hosting the best replica of specific content.  The
challenge resides in handling concurrent operations that may impair
the propagation of messages, and in turns, lead to inconsistent
partitioning. 
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

As future work, we plan on extending the logical partitioning protocol
to enable lazy retrieval of partitions. Indeed, using \NAME, every
\process partakes in the propagation of indexes of content and
replicas. We would like to leverage the hierarchical properties of
interconnected autonomous systems to limit the propagation of such
indexes only to interested systems.
%
%% As ongoing and future work, we are currently studying how it might be
%% possible to limit the scope of a partition to one autonomous system at
%% most. Indeed, the gain of propagating changes to \processes belonging to
%% another autonomous system might be negligible as the latency penalty
%% is mainly due to inter autonomous systems' links (\eg trans-continental
%% links).  Exactly, we are investigating how such a change can be
%% formalized and its impact on the current protocol.
%
%autonomous systems. Indeed, \processes could leverage the hierarchical
%properties of the Internet topology~\cite{nur2018geography} to avoid
%flooding the whole systems with control information about all
%partitions.
%\TODO{should we highlight this at the end of the experiment}
%

\noindent We also would like to evaluate \NAME within a concrete
storage systems such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of \NAME in a real system subject to high dynamicity, and
compare it against its current DHT-based indexing system that does not
include distance in its operation.

%% Such an integration would enable us to to perform additional
%% experiments and observe the gain with respect to the DHT-based
%% approach that is currently used.

%% In addition to this action, it would make sense to evaluate
%% the use of \NAME within a concrete storage systems, such as
%% \underline{I}nter\underline{P}lanetary \underline{F}ile
%% \underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
%% integration would enable us to to perform additional experiments and
%% observe the gain with respect to the DHT-based approach that is
%% currently used.

### 2021-04-23 input/proposal.tex
reworkd conclusion

Unfortunately, \processes do not share a common global knowledge of
the network state. For \processes to reach consistent partitioning
together, a \process becoming a source must notify every \process that
is closer to it than any other source. Since epidemic dissemination
and scoped broadcast have well-aligned preoccupations, we assume
implementations relying on forwarding of messages from
neighbor-to-neighbor.

>>>>

Unfortunately, \processes do not share a common global knowledge of
the network state. For \processes to reach consistent partitioning
together, a \Process $s$ becoming a source must send a notification
$\alpha_s$ to every \process that is closer to it than any other
source. Since epidemic dissemination and scoped broadcast have
well-aligned preoccupations, we assume implementations relying on
forwarding of messages from neighbor-to-neighbor.

### 2021-04-23 input/related_work.tex
mostly implemand algo + transi xpe to related work
reworkd conclusion

\vfill
\TODO{spacing}
\newpage

\section{Related Work}
\label{sec:related_work}
Content indexing in geo-distributed infrastructures has been studied through various approaches. 
Offering an indexing service which is either hosted by a centralized entity or distributed through nodes of the network has long been the predominant one. This mainly requires (i) to have access to the list of current replica locations and (ii) to be aware of the topology to compute which replica is the closest for a given location.

@@

(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica. Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings. This is a well-studied problem in the network community and numerous protocols have been proposed. As for the index, this knowledge about the topology can be either centralized~\cite{topology-discovery} or distributed like in routing protocols such as \underline{O}pen \underline{S}hortest \underline{P}ath \underline{F}irst (OSPF).

All these solutions require to contact a remote node (either a server or a DHT node) to request this index 
which is costly in terms of latency while in contradiction with Edge infrastructure constraints, as previsouly explained.

The opposite approach consists in hosting the index directly on the nodes, avoiding any prior request to access a content.   
%This requires notifying nodes of replica creations and removals along with information about the evolving topology. 
Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica locations for all nodes, as usually implemented in \underline{N}amed \underline{D}ata \underline{N}etworking (NDN)~\cite{nlsr}.  Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily determine where the closest copy of a given object resides, without contacting any remote node.
Similarly, one could solve this issue by using a \underline{C}onflict-\underline{F}ree \underline{R}eplicated \underline{D}atatype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. Yet both solutions inherently imply that every node will eventually receive all messages.

At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create a scope-related partioning, as proposed in this paper. Such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology. Moreover, membership protocols are usually implemented  by modifying the neighboring of a given node according to a certain metric in a logical overlay.
On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed. Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change. Likewise, this also prevents from using solutions that periodically advertise their cache content~\cite{garcia-lopez, hemmati2015namebased} as they also inccur an overhead even in quiet contexts without any update. 
Moreoever, such solutions necessarily rely on physical timeouts that could lead to either premature removals of partitions when they are still operating; or slow convergence where processes wrongly believe they belong to a partition that was removed.

%Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
%On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica. This enables for a request to be caught \textit{on-path}, and be redirected to the closest replica. However, the announcement is only performed towards this original replica, that is requests can miss closer replicas that are not on this path, thus decreasing the efficiency of the cache sharing mechanism.

%AVK: This should go where we explain the DEL, as this is really specific...
%One could also solve this issue by removing partitions that were not advertised for a defined time~\cite{hemmati2015namebased, garcia-lopez}. 
%However, relying on physical timeout could lead to either premature removals of partitions when they are still operating; or slow convergence where processes believe they belong to a partition that was removed (\TODO{plot ?}). In addition, since timeouts imply a
%continuous maintenance of partitions, such partitioning protocol
%incurs an overhead even in quiet contexts without dynamic partitions.

% AVK
% t-man: T-Man: Gossip-Based Overlay Topology Management5doat a random time 
% at a random time once in eachconsecutive interval of T time unit
% This buffer contains a random sample of the nodes from the entirenetwork. It is provided by apeer sampling service
% 
% We do not try to to create a topology aware overlay ! Because locality.
% We do not provide routing ! routing is two determine path between any pair of nodes. We only provide path to objects 
% 
% Koala locality aware routing. Long links. Lazzy (nothing happens)
% Koala  shares  many  core  aspectswith similar overlays, such as Chord and Symphony.
% 
% VoroNet: overlay and routing. i.e. long links 
% It links application objects rathen than physical nodes so that objects with similar characteristic are neighbors. 
% are logigal overlay, that are not correlated to the physical infrstructure. 
% Usually rely on long links...
% AVK

%% \begin{definition}[Dynamic optimal partitioning]
%%   A dynamic optimal partitioning is an optimal partitioning where the
%%   set of sources $S$ does not monotonically increase. We suffix this
%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
%%   of sources by \underline{a}dding its partition with messages
%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
%%   leaves the set of sources by \underline{d}eleting its partition with
%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
%% \end{definition}

%% Unfortunately, due to differences in receipt order of messages between
%% processes, stale information may stop prematurely the propagation of
%% relevant messages leading to inconsistent partitioning.
%% \TODO{Figure~\ref{fig:del} shows that.}
% 
% One could solve this issue by using a conflict-free replicated data
% type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
% require eventual delivery of messages to ensure convergence. All
% processes need to receive, deliver, hence broadcast all
% operations. Some processes may receive operations unnecessary to their
% correct functioning, for these operations did not happen in their
% locality.  One could also solve this issue by removing partitions that
% were not advertised for a defined
% time~\cite{hemmati2015namebased}. \TODO{check distance-vector
%   protocols.} However, relying on physical timeout could lead to
% either premature removals of partitions when they are still operating;
% or slow convergence where processes believe they belong to a partition
% that was removed (\TODO{plot ?}). In addition, since timeouts imply a
% continuous maintenance of partitions, such partitioning protocol
% incurs an overhead even in quiet contexts without dynamic partitions.

%% \begin{problem}[\label{prob:intra}Consistent partitioning]
%%   How to enable \emph{consistent} dynamic optimal partitioning in
%%   dynamic network using scoped flooding?
%% \end{problem}

% \TODO{Dynamic Multiple-sources All-destinations shortest path on
%  dynamic graphs?}

%% \begin{figure}
%%   \begin{center}
%%     \input{input/figASmotivation.tex}
%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
%%       objects, processes do not know about all partitions that exist
%%       in the whole distributed system.}
%%   \end{center}
%% \end{figure}

%% To further improve scoped flooding in autonomous systems, processes
%% may belong to multiple partitions representing the objects they are
%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
%% nature of autonomous systems. Autonomous systems have topological
%% properties~\cite{nur2018geography} that processes can leverage to
%% avoid flooding the whole systems with control information about all
%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
%% partition about a specific object, flooding Paris's AS to notify
%% neighboring processes of the object. However, it does not flood the
%% whole network, for control information stops at Process $b$. It
%% significantly saves bandwidth compared to broadcast since processes
%% below entrypoints of autonomous systems are order of magnitude more
%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
%% to return an object they are unaware of. Processes remain efficient in
%% answering requests. \TODO{which is important for end users \REF.}

%% \begin{definition}[Partitions in asynchronous systems]
%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
%%   \TODO{TODO} \TODO{or multi-partitioning?}
%% \end{definition}

%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
%%   How to enable scoped flooding of objects in autonomous systems?
%% \end{problem}

%% Next Section presents our approach that solves these scientific
%% problems by relying on logical control information only.

>>>>

\section{Related Work}
\label{sec:related_work}

Content indexing in geo-distributed infrastructures has been studied
through various approaches.  Offering an indexing service which is
either hosted by a centralized entity or distributed through nodes of
the network has long been the predominant one. This mainly requires
(i) to have access to the list of current replica locations and (ii)
to be aware of the topology to compute which replica is the closest
for a given location.

@@

(ii) Being centralized or distributed, this index should be enhanced
with the topology knowledge in order to be able to decide where
resides the closest replica. Maintaining a consistent view of an ever
changing topology across a network is inherently complicated,
especially in asynchronous settings. This is a well-studied problem in
the network community and numerous protocols have been proposed. As
for the index, this knowledge about the topology can be either
centralized~\cite{topology-discovery} or distributed like in routing
protocols such as \underline{O}pen \underline{S}hortest
\underline{P}ath \underline{F}irst (OSPF).

All these solutions require to contact a remote node (either a server
or a DHT node) to request this index which is costly in terms of
latency while in contradiction with Edge infrastructure constraints,
as previously explained.

The opposite approach consists in hosting the index directly on the
nodes, avoiding any prior request to access a content.
%This requires notifying nodes of replica creations and removals along
%with information about the evolving topology.
Broadcasting information about cache updates to all nodes in the
system is a straightforward way to maintain consistent information
about replica locations for all nodes, as usually implemented in
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr}.  Indeed, having the entire knowledge of all the
replica localization along with distance information carried into
messages, each node can easily determine where the closest copy of a
given object resides, without contacting any remote node.  Similarly,
one could solve this issue by using a
\underline{C}onflict-\underline{F}ree \underline{R}eplicated
\underline{D}atatype (CRDT) for set data structures, for
example~\cite{shapiro2011crdts}. Yet both solutions inherently imply
that every node will eventually receive all messages.

At first glance, membership protocols as proposed in~\cite{t-man}
would appear to provide suitable abstractions to create a
scope-related partitioning, as proposed in this paper. Such protocols
usually rely on gossip mechanism, implying contacts with random nodes
that can be very far away in the physical topology. Moreover,
membership protocols are usually implemented by modifying the
neighboring of a given node according to a certain metric in a logical
overlay.  On the contrary, we do not aim at building any overlay, as
we only rely on the physical topology so the neighbors of a given node
are not continuously modified. Lastly, these protocols are usually
cycle-based, meaning that they impose a constant load on the network
traffic, even when the system state does not change. Likewise, this
also prevents from using solutions that periodically advertise their
cache content~\cite{garcia-lopez, hemmati2015namebased} as they also
incur an overhead even in quiet contexts without any update.
Moreover, such solutions necessarily rely on physical timeouts that
could lead to either premature removals of partitions when they are
still operating; or slow convergence where processes wrongly believe
they belong to a partition that was removed.

%Finally, we emphasize that consistency is at the core of our design,
%as \NAME provides the same guarantees for all nodes.  On the
%contrary, to avoid flooding, authors in~\cite{opnl} propose to
%propagate information about cache updates only towards the original
%replica. This enables for a request to be caught \textit{on-path},
%and be redirected to the closest replica. However, the announcement
%is only performed towards this original replica, that is requests can
%miss closer replicas that are not on this path, thus decreasing the
%efficiency of the cache sharing mechanism.

%AVK: This should go where we explain the DEL, as this is really
%specific...  One could also solve this issue by removing partitions
%that were not advertised for a defined
%time~\cite{hemmati2015namebased, garcia-lopez}.  However, relying on
%physical timeout could lead to either premature removals of
%partitions when they are still operating; or slow convergence where
%processes believe they belong to a partition that was removed
%(\TODO{plot ?}). In addition, since timeouts imply a continuous
%maintenance of partitions, such partitioning protocol incurs an
%overhead even in quiet contexts without dynamic partitions.

% AVK t-man: T-Man: Gossip-Based Overlay Topology Management5doat a
% random time at a random time once in eachconsecutive interval of T
% time unit This buffer contains a random sample of the nodes from the
% entirenetwork. It is provided by apeer sampling service We do not
% try to to create a topology aware overlay ! Because locality.  We do
% not provide routing ! routing is two determine path between any pair
% of nodes. We only provide path to objects Koala locality aware
% routing. Long links. Lazzy (nothing happens) Koala shares many core
% aspectswith similar overlays, such as Chord and Symphony.  VoroNet:
% overlay and routing. i.e. long links It links application objects
% rathen than physical nodes so that objects with similar
% characteristic are neighbors.  are logigal overlay, that are not
% correlated to the physical infrstructure.  Usually rely on long
% links...  AVK
